A Modern Take on Renormalization

### 2023-03-04 beta/Renormalization/wilson.tex
Add minor updates to various notes
Add minor updates on Wilsonian RG

	\begin{itemize}[parsep=0pt,itemsep=.5\parskip,labelindent=.1\parindent]
	\item David Skinner's note:
	  \begin{itemize}[nosep]
	  \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT.html}
	    \begin{itemize}[nosep]
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/Wilsonchap.pdf}
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/chap5.pdf}
	    \end{itemize}
	  \end{itemize}
	\item Schwartz, Chapter 15
	\item Peskin \& Schroeder, Chapter 10, 11 \& 12
	\item Hollowood's book:
	  \begin{itemize}[nosep]
	  \item \url{https://arxiv.org/abs/0909.0859}
	  \item \url{https://link.springer.com/book/10.1007/978-3-642-36312-2}
	  \end{itemize}
	\end{itemize}

@@

	The path integral measure, however, is \textit{not} scale-invariant; we have to add back some Fourier modes in between to return the path integral back to $\Lambda_0$. Luckily, the additional modes happen to cancels out the $Z_\phi$ factor in \eqref{eq:PI_free}:
	\begin{equation}
		\sqrt{Z_\phi^\#} \DD\phi^{\Lambda}
		\sim \sqrt{Z_\phi^\#}
			\prod_{\norm{p} < \Lambda = s\Lambda_0}
			\dd{\tilde{\phi}(p)}
		= \prod_{\norm{p'} < \Lambda_0}
			\dd{\tilde{\phi}'(p')}
		\sim \DD\phi'^{\,\Lambda_0}
	\end{equation}
	Therefore the complete path integral is invariant under coarse-graining \& rescaling. $Z_\phi$ is also unchanged during this process. Therefore we can simply set $Z_\phi \equiv 1$ by an appropriate \textit{normalization} of $\phi$.

@@

	In particular, the coefficient $
		\frac{\var[2]{i\Gamma}}{
			\var{\varphi(x_1)} \var{\varphi(x_2)}
		}
	$ of the $\varphi^2$ vertex is precisely minus the inverse of the full propagator, i.e. for scalar fields:
	\begin{equation}
		i\,(\pd^2-m^2) \sim -i\,(p^2 + m^2)
	\end{equation}
	Here $m$ is the renomalized mass $m$. In general the terms in $\Gamma[\varphi]$ are the \textit{renomalized vertices}, which pack up all higher loop quantum corrections. Diagrammatically, they are produced by the one particle irreducible (1PI) diagrams.

>>>>

	\begin{itemize}[parsep=0pt,itemsep=.5\parskip,labelindent=.1\parindent]
	\item David Skinner's note:
	  \begin{itemize}[nosep]
	  \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT.html}
	    \begin{itemize}[nosep]
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/Wilsonchap.pdf}
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/chap5.pdf}
	    \end{itemize}
	  \end{itemize}
	\item Zee, III.1
	\item Schwartz, Chapter 15
	\item Srednicki, Chapter 29, \textit{Effective field theory}
	\item Peskin \& Schroeder, Chapter 10, 11 \& 12
	\item Hollowood's book:
	  \begin{itemize}[nosep]
	  \item \url{https://arxiv.org/abs/0909.0859}
	  \item \url{https://link.springer.com/book/10.1007/978-3-642-36312-2}
	  \end{itemize}
	\end{itemize}

@@

	The path integral measure, however, is generally not scale-invariant; we have to add back some Fourier modes in between to return the path integral back to $\Lambda_0$. Luckily, in the case of a massless free scalar on a flat background, the additional modes happen to cancels out the $Z_\phi$ factor in \eqref{eq:PI_free}:
	\begin{equation}
		\sqrt{Z_\phi^\#} \DD\phi^{\Lambda}
		\sim \sqrt{Z_\phi^\#}
			\prod_{\norm{p} < \Lambda = s\Lambda_0}
			\dd{\tilde{\phi}(p)}
		= \prod_{\norm{p'} < \Lambda_0}
			\dd{\tilde{\phi}'(p')}
		\sim \DD\phi'^{\,\Lambda_0}
	\end{equation}
	Therefore the complete path integral is invariant under coarse-graining \& rescaling. $Z_\phi$ is also unchanged during this process. Therefore we can simply set $Z_\phi \equiv 1$ by an appropriate \textit{normalization} of $\phi$.

@@

	In particular, the coefficient $
		\frac{\var[2]{i\Gamma}}{
			\var{\varphi(x_1)} \var{\varphi(x_2)}
		}
	$ of the $\varphi^2$ vertex is precisely minus the inverse of the full propagator, i.e. for scalar fields:
	\begin{equation}
		i\,(\pd^2-m^2) \sim -i\,(p^2 + m^2)
	\end{equation}
	Here $m$ is the renomalized mass $m$. In general the terms in $\Gamma[\varphi]$ are the \textit{renomalized vertices}, which pack up all higher loop quantum corrections. Diagrammatically, they are produced by the one particle irreducible (1PI) diagrams. Roughly speaking, we have:
	\begin{equation}
		\log \sum \,(\text{all diagrams})
		\sim \sum \,(\text{connected diagrams})
		\sim \sum \,(\text{tree with 1PI vertices})
	\end{equation}
